Notes

### 2023-08-16 Notes.Rmd
draft report to share with collabs

>>>>

*230816*

- Created a report with preliminary data from Lloyds and Orbis. 
- Data from Kroodsma was used to identify >16k vessels fishing in places prone to tipping
- Places were extracted from Smith heatwaves methodology replicated on NOAAs temp data and my dataset on resilience loss
- > 2000 companies identified, and >700 shareholders, but networks are too sparse
